BlueTracer: \\ a Robust API Tracer for Evasive Malware

### 2018-07-14 Msc-Slides/main.tex
Thesis grammar fixes
Slides in progress

@@

@@

A dynamic binary analysis
technique in which the behaviour of an application is inspected at run-time via the
injection of analysis code. 
\bigskip
\begin{block}{}
\begin{lstlisting}[basicstyle=\ttfamily\large,xleftmargin=50pt]
<@\textcolor{red}{record(arg1)}@> 
retval = libcall(arg1, &arg2)
<@\textcolor{red}{record(retval, *arg2)}@> 
\end{lstlisting}
\end{block}
\bigskip
\textbf{Problem 1}: existing products have limited logging capabilites

@@

@@

\begin{frame}
    \frametitle{Intel Pin}

@@

>>>>

    \begin{textblock*}{2cm}(9.0cm,-6.5cm)
   \includegraphics[width=1.2cm]{image/search.png}% use the \includegraphics command here
	\end{textblock*}

@@

    \begin{textblock*}{2cm}(8.3cm,-3cm)
   \includegraphics[width=2cm]{image/hook.png}% use the \includegraphics command here
	\end{textblock*}

@@

A dynamic binary analysis
technique in which the behaviour of an application is inspected at run-time via the
injection of analysis code. 
\bigskip
\begin{block}{}
\begin{lstlisting}[basicstyle=\ttfamily\large,xleftmargin=50pt]
<@\textcolor{red}{record(arg1)}@> 
retval = libcall(arg1, &arg2)
<@\textcolor{red}{record(retval, *arg2)}@> 
\end{lstlisting}
\end{block}
\bigskip
\bigskip
\textbf{Problem 1}: existing products have limited logging capabilites

@@

\begin{beamerboxesrounded}[shadow=true]{}
\textbf{BlueTracer} is a robust library and system call tracer for Windows programs specialized in evasive malware
\end{beamerboxesrounded}

\bigskip

Implementation details:
\begin{itemize}
\item Based on the \textbf{Intel Pin} DBI framework
\item Integrated with the \textbf{BluePill} stealthy execution framework
\item Combines reliable external sources of prototypes information
\end{itemize}

\bigskip

Key features:
\begin{itemize}
\item Undetected tracing of input parameters, output buffers and return values of over 17 000 system calls and library calls
\item Logging of asynchronous events
\item Resolution of named constants
\end{itemize}

@@

\begin{frame}
    \frametitle{Why Intel Pin ?}

	Characteristics:
	\begin{itemize}
	\item \textbf{User-friendliness}
	\item \textbf{Portability}
	\item \textbf{Transparency}
	\item \textbf{Efficiency}
	\end{itemize}
	\bigskip
	\textbf{Analysis routines:} embody the code to be inserted during the application's execution\\
	\smallskip
	\textbf{Instrumentation routines:} determine where the analysis code has to be placed\\
	\bigskip
	Different analysis and instrumentation granularities
	\begin{itemize}
	\item Instruction, trace, routine and image
	\end{itemize}

    \begin{textblock*}{3cm}(6cm,-6.5cm)
   \includegraphics[width=1.6cm]{image/pin.png}% use the \includegraphics command here
	\end{textblock*}

@@

    \begin{figure}
    	\vspace{-0.5cm}
    	%\hspace*{1cm}
        \includegraphics[width=11cm]{image/BlueTracer.pdf}
    \end{figure}
